Constraint Programming - Inside Gecode

### 2014-05-04 paper.tex
conclusion

	\section{Conclusion}
	\textit{conclusion}

>>>>

	\section{Conclusion}
	Constraint programming is a very useful tool in practice, as it can solve abritrary combinatorial or optimization problems. Gecode, as representant of the various toolsets, implements a very hand interface to transform a mathematical description of a problem into code, which then can be used to solve the problem. In conclusion Gecode provides all the necessary tools, combines them with a nice interface, and is still very flexible concering optimzation for a certain area through the possibility to implement custom search strategies, based on some well studied and efficient algorithms.
